---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub
We will subset the data by sex to see if the drug is sex specific

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
 
   The percentage of people getting aids doesn't change significatly between taking the drug or taking the pacebo. 

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```
We fail to reject the null hypothesis, the p-Value is almost 50%, so this happens about 50% of the time. 


```{r}
chisqtestGC(tabinfgroall)
```
The p-Value of .5735 says that if the null hypothesis is true, we should expect results like this about 57% of the time. This is not enough evidence to reject the null hypothesis, so we are going to fail to reject it. 

```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabingromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabingromale,type="percent")
```

```{r}
rowPerc(tabingromale)
colPerc(tabingromale)
```

```{r}
chisqtestGC(tabingromale)
```


```{r}
infgrofemale <- filter(Genvoyabub,sex == "F")
tabinfgrofemale <-xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```


```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```

```{r}
chisqtestGC(tabinfgrofemale)
```


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.




# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






