---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub
We will subset the data by sex to see if the drug is sex specific

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
 
   The percentage of people getting aids doesn't change significatly between taking the drug or taking the pacebo. As the chart shows there is almost no diference on the people that didn't get aids, who took the drug or who took the placebo. The same situation for the people who took the drugs, there is proably a 5 percent higher in those who took the drug than those who took the placebo.

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```
The Percentage shown here demonstrate that it didn't make a significant difference wether the people took the placebo or the drugs. 

```{r}
chisqtestGC(tabinfgroall)
```
The p-Value of .5735 says that if the null hypothesis is true, we should expect results like this about 57% of the time. This is not enough evidence to reject the null hypothesis, so we are going to fail to reject it. 

```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabingromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabingromale,type="percent")
```
The charts show that there is no suffcient evidence of the difference the drug or the placebo made on Males. The aids chart is about 1% difference between those who took the placebo and those who took the drug. For the males that didn't get aids, it made no difference at all whether they took the placebo or the drug. 





```{r}
rowPerc(tabingromale)
colPerc(tabingromale)
```




```{r}
chisqtestGC(tabingromale)
```


```{r}
infgrofemale <- filter(Genvoyabub,sex == "F")
tabinfgrofemale <-xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```


```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```

```{r}
chisqtestGC(tabinfgrofemale)
```


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
atripall<- xtabs(~infected+group,data=Atriplavast)
barchartGC(atripall,type="percent")
```
 
 It appears that the number of people who took the Atriplavast had  smaller possibility of getting aids then those who took the placebo. For those who didn't get aids, it didn't make a difference wether they had the Atriplavast or the placebo.    
 
 
 
 
 
```{r}
rowPerc(atripall)
colPerc(atripall)
```

This data shows that there is a difference of about 6% between those who got aids and took the drug, then those who took the placebo. For those who didn't take the placebo or the drug, the possibility of getting aids appears to be the same.   


```{r}
chisqtestGC(atripall, graph=TRUE)
```

We do not have enough evidence to reject the null hypothesis so we fail to reject it.  It shows that every time we make this test we will get the same results 6 percent of the time. 



```{r}
atripM<- filter(Atriplavast,sex=="M")
atripM2<- xtabs(~infected+group,data=atripM)
barchartGC(atripM2,type="percent")
```

This graph shows that the percentage of Males who got aids is lower for those who took the drug then those who took the placebo. For those who didn't get aids, it didn't make a difference if they took the placebo or the drug. 


```{r}
rowPerc(atripM2)
colPerc(atripM2)
```

This data shows that the Males who took the drug had about 50% less chance of getting aids versus the ones who took the placebo. As for the males that didn't get aids, it didn't make a difference if they took the drug or the placebo.

```{r}
chisqtestGC(atripM2,graph=TRUE)
```

This test shows that there is enough evidence to reject the null hypothesis. 




```{r}
atripF<- filter(Atriplavast,sex=="F")
atripF2<- xtabs(~infected+group,data=atripF)
barchartGC(atripF2,type="percent")
```

This chart shows that the percentage of Females who got aids and took the drug is higher then those who got aids and took the placebo. This shows that the drug has no effect on preventing aids. For the Females who didn't get aids, it didn't make a difference if they took the drug or the placebo.


```{r}
rowPerc(atripF2)
colPerc(atripF2)
```
This data shows that the drug is making no difference in preventing aids because the perecentage of Females getting aids is higher for those who took the drug versus those who took the placebo.   



```{r}
chisqtestGC(atripF2,graph=TRUE)
```

This test shows that there is enough evidance to reject the null hypothesis. 




# abacavirinol

We will subset the data by sex to see if the drug is sex specific.

```{r}
Abacaall<- xtabs(~infected+group,data=abacavirinol)
barchartGC(Abacaall,type="percent")

```

The chart shows that the drug makes no diference for those who got aids or for those who didn't get aids. 

```{r}
rowPerc(Abacaall)
colPerc(Abacaall)
```

This data shows that the drug didn't make an impact on preventing aids. The same number of people that got aids took the drug and the placebo.

```{r}
chisqtestGC(Abacaall, graph=TRUE)
```

The results of this test give a P-Value of .8942 percent, which means that we will get this same result about 89% of the time. We do not have enough evidence to reject the null hypothesis, therefore we fail to reject the null hypothesis.


```{r}
abacamale<- filter(abacavirinol,sex=="M")
abacamale2<- xtabs(~infected + group, data=abacamale)
barchartGC(abacamale2,type="percent")
```

This chart shows that the drug is having no effect on preventing aids. The percentage of the Males who got aids is higher for those who took the drug then for those who took the placebo. For those who didn't get aids, there is no difference if they took the placebo and the drug.


```{r}
rowPerc(abacamale2)
colPerc(abacamale2)
```

This data shows that the drug has no effect on preventing aids. The percentage of the people who got aids is higher for those who took the drug then for the ones who took the palcebo. It appears that the drug is influencing on males getting aids.


```{r}
chisqtestGC(abacamale2, graph=TRUE)
```

There is no significant evidence, the P-Value of .09 makes us fail to reject the null hypothesis. 


```{r}
abacafemale<- filter(abacavirinol,sex=="F")
abacafemale2<- xtabs(~infected + group, data=abacafemale)
barchartGC(abacafemale2,type="percent")
```

This chart shows that the Females percentage of those who got aids is lower for those who took the drug versus those who took the placebo. For the females who didn't get aids, it didn't make a difference for those who took the drug or the placebo.


```{r}
rowPerc(abacafemale2)
colPerc(abacafemale2)
```

This data shows that the drug does help Females prevent aids. The percentage of Females who got aids and took the placebo is twice a high then those who took the drug and got aids. 

```{r}
chisqtestGC(abacafemale2, graph=TRUE)
```

This test shows that we have enough evidence to reject the null hypothesis. 




