---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub
We will subset the data by sex to see if the drug is sex specific

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
 
   The percentage of people getting aids doesn't change significatly between taking the drug or taking the pacebo. 

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```
We fail to reject the null hypothesis, the p-Value is almost 50%, so this happens about 50% of the time. 


```{r}
chisqtestGC(tabinfgroall)
```
The p-Value of .5735 says that if the null hypothesis is true, we should expect results like this about 57% of the time. This is not enough evidence to reject the null hypothesis, so we are going to fail to reject it. 

```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabingromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabingromale,type="percent")
```

This chart show that it made no difference for the Males who took the Genvoyabun drug and got aids and those who didn't get aids and didn't take the drug. 



```{r}
rowPerc(tabingromale)
colPerc(tabingromale)
```

This data shows that the Males who took the drug or the placebo had the same chance of getting aids. Taking the drug had no significant difference then those who took the placebo and didn't get aids. 


```{r}
chisqtestGC(tabingromale,graph=TRUE)
```

This test shows that there is no significant evidence to reject the null hypothesis, so we fail to reject the null hypothesis. The p-value shows that we will get this same results 100% of the time. 



```{r}
infgrofemale <- filter(Genvoyabub,sex == "F")
tabinfgrofemale <-xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```

The chart shows little differnce between the percent of Females who took the drug and got aids and the percentage who took the placebo and got aids. It show that for the females who didn't get aids, it didn't make a difference wether they took the drug or the placebo. 



```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```





```{r}
chisqtestGC(tabinfgrofemale)
```





# Atriplavast

We will subset the data by sex to see if the drug is sex specific.




# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






