---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub
We will subset the data by sex to see if the drug is sex specific

```{r}
tabinfgroall<- xtabs(~infected+group,data=Genvoyabub)
barchartGC(tabinfgroall,type="percent")
```
 
   The percentage of people getting aids doesn't change significatly between taking the drug or taking the pacebo. As the chart shows there is almost no diference on the people that didn't get aids, who took the drug or who took the placebo. The same situation for the people who took the drugs, there is proably a 5 percent higher in those who took the drug than those who took the placebo.

```{r}
rowPerc(tabinfgroall)
colPerc(tabinfgroall)
```
The Percentage shown here demonstrate that it didn't make a significant difference wether the people took the placebo or the drugs. 

```{r}
chisqtestGC(tabinfgroall)
```
The p-Value of .5735 says that if the null hypothesis is true, we should expect results like this about 57% of the time. This is not enough evidence to reject the null hypothesis, so we are going to fail to reject it. 

```{r}
infgromale<- filter(Genvoyabub,sex=="M")
tabingromale<- xtabs(~infected+group,data=infgromale)
barchartGC(tabingromale,type="percent")
```
The charts show that there is no suffcient evidence of the difference the drug or the placebo made on Males. The aids chart is about 1% difference between those who took the placebo and those who took the drug. For the males that didn't get aids, it made no difference at all whether they took the placebo or the drug. 





```{r}
rowPerc(tabingromale)
colPerc(tabingromale)
```




```{r}
chisqtestGC(tabingromale)
```


```{r}
infgrofemale <- filter(Genvoyabub,sex == "F")
tabinfgrofemale <-xtabs(~infected+group,data=infgrofemale)
barchartGC(tabinfgrofemale,type="percent")
```


```{r}
rowPerc(tabinfgrofemale)
colPerc(tabinfgrofemale)
```

```{r}
chisqtestGC(tabinfgrofemale)
```


# Atriplavast

We will subset the data by sex to see if the drug is sex specific.

```{r}
atripall<- xtabs(~infected+group,data=Atriplavast)
barchartGC(atripall,type="percent")
```
 
 It appears that the number of people who took the Atriplavast had a smaller possibility of getting aids then those who took the placebo. For those who didn't get aids, it didn't make a difference wether they had the Atriplavast or the placebo.    
 
 
 
 
 
```{r}
rowPerc(atripall)
colPerc(atripall)
```

This data shows that there is a difference of about 6% between those who got aids and took the drug, then those who took the placebo. For those who didn't take the placebo or the drug, the possibility of getting aids appears to be the same.   


```{r}
chisqtestGC(atripall, graph=TRUE)
```

We do not have enough evidance to reject the null hypothesis so we fail to reject it.   



```{r}
atripM<- filter(Genvoyabub,sex=="M")
atripM2<- xtabs(~infected+group,data=atripM)
barchartGC(atripM2,type="percent")
```



This graph shows no significant difference between the Males who got aids and got the placebo and the Males who got aids and took the drug. I appears that the drug it's not making a differnce, on preventing aids.    




```{r}
rowPerc(atripM2)
colPerc(atripM2)
```

This data shows that the same number of people who got aids took the placebo and  the drug got aid and that the same number of males who didn't take either of them, got aids.   


```{r}
chisqtestGC(atripM2,graph=TRUE)
```

This test show that there is not a strong evidence against the null hypothesis, therefore we fail to reject it.   




```{r}
atripF<- filter(Genvoyabub,sex=="F")
atripF2<- xtabs(~infected+group,data=atripF)
barchartGC(atripF2,type="percent")
```

This chart shows that there is a slight difference between the Females who got aids and the females who didn't get aids. It appears that the drug is making no significant difference in preventing aids.     



```{r}
rowPerc(atripF2)
colPerc(atripF2)
```
This data shows that there is less then 1% difference in the number of Females who got aids and took the Atriplavast drug and those who got aids and took the placebo. It show that there is no difference in those who got aids and didn't take the placebo or the drug.   



```{r}
chisqtestGC(atripF2,graph=TRUE)
```

This test shows that everytime we do this, we will get the same results 50% of the time. The evidence is not significaant and we fail to reject the null hypothesis.   




# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






